\textbf{\sc Towards Deliberative Control in Marine Robotics}

### 2012-02-24 arch.tex
added figures to illustrate reactor failure to synchronize

Take for example our AUV agent from Fig. \ref{fig:agent},
and assume that the \texttt{Sampling} reactor failed to synchronize;
in  such case this reactor is destroyed and both
\texttt{Sampling\_policy} and \texttt{Relevant\_data} state variables
produced the \texttt{Failed} observation. Therefore, the
\texttt{Survey controller} will received this observation on its {\em
  external} \texttt{Sampling\_policy} which indicates that this state
variable is not managed anymore. At this point depending on this
reactor implementation we have two possible outcomes:
\begin{enumerate}
\item \texttt{Survey  controller} model allows him to integrate this
  \texttt{Failed} observation. For example it can identify that, from
  now on, there's no way to take water samples. It still can 
  navigate as \texttt{Pilot} is available which allow him to continue
  this aspect of its current plan.
\item \texttt{Survey controller} models is not able to handle this
  unexpected failure resulting in turn on its failure to
  synchronize. This result on this reactor being also destroyed and
  the \texttt{Failed} observation is produced on the \texttt{survey}
  timeline.
\end{enumerate}
Even on the worst case scenario presented on this second case, we
note that a reactor failure only propagates up in the reactor graph. 
In our example, even if all the reactors that depends on
\texttt{Sampling} are entrained by its failure, we still keep the
three reactors \texttt{Vehicle}, \texttt{Pilot} and \texttt{Ship
  operation} allowing to  maintain the vehicle navigation control
(\texttt{Pilot}) along with high level safety operation 
(\texttt{Ship operation}). It illustrates how \rx can handle graceful
system degradation despite the failure of one or more reactors. It
also emphasize that it is critical to ensure that the low level
reactors are properly designed in order to be as robust as 
possible.

>>>>

Take for example our AUV agent from Fig. \ref{fig:agent},
and assume that the \texttt{Sampling} reactor failed to synchronize;
in  such case this reactor is destroyed and both
\texttt{Sampling\_policy} and \texttt{Relevant\_data} state variables
produced the \texttt{Failed} observation as illustrated in in
Fig. \ref{fig:fail0}. Therefore, the
\texttt{Survey controller} will received this observation on its {\em
  external} \texttt{Sampling\_policy} which indicates that this state
variable is not managed anymore. At this point depending on this
reactor implementation we have two possible outcomes:
\begin{enumerate}
\item \texttt{Survey  controller} model allows him to integrate this
  \texttt{Failed} observation. For example it can identify that, from
  now on, there's no way to take water samples. It still can 
  navigate as \texttt{Pilot} is available which allow him to continue
  this aspect of its current plan. In such case the agent structure
  remains as in Fig. \ref{fig:fail0} with no further impact.
\item \texttt{Survey controller} models is not able to handle this
  unexpected failure resulting in turn on its failure to
  synchronize. This result on this reactor being also destroyed and
  the \texttt{Failed} observation is produced on the \texttt{survey}
  timeline (Fig. \ref{fig:fail1}).
\end{enumerate}
\begin{figure}[!htb]
  \centering
  \subfloat[\small When \texttt{Sampling} reactor fails to
  synchronize its removed from the graph and all its {\em internal}
  timelines produces the \texttt{Failed} observation]{\includegraphics[width=0.4\columnwidth]{figs/AUV-fail0.pdf}
  \label{fig:fail0}
  }
  \qquad
  \subfloat[\small In the worst case this \texttt{Failed} may imply
  other reactors hat depends on \texttt{Sampling} to  fail to
  synchronize implying a bottom-up destruction of faulty reactors.]{
    \includegraphics[width=0.4\columnwidth]{figs/AUV-fail1}
    \label{fig:fail1}
  }
  \caption{Impact of the \texttt{Sampling} reactor failure in the AUV
    agent from Fig. \ref{fig:agent}}
\end{figure}

Even on the worst case scenario presented on this second case, we
note that a reactor failure only propagates up in the reactor graph. 
In our example, even if all the reactors that depends on
\texttt{Sampling} are entrained by its failure, we still keep the
three reactors \texttt{Vehicle}, \texttt{Pilot} and \texttt{Ship
  operation} allowing to  maintain the vehicle navigation control
(\texttt{Pilot}) along with high level safety operation 
(\texttt{Ship operation}). It illustrates how \rx can handle graceful
system degradation despite the failure of one or more reactors. It
also emphasize that it is critical to ensure that the low level
reactors are properly designed in order to be as robust as 
possible.
